---
title: "Load project files and their metadata"
author: "Marija Gacic"
date: "2024-07-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# library(sbShinyModules)
```

## File loading via SBGFS in Data Studio infrastructure

The `get_all_project_files()` is a utility function for loading project files   and their metadata when developing Shiny apps within Data Studio, 
or deploying as on-demand Shiny apps using Data Studio infrastructure.

Data Studio - [placeholder for more details about the files organization on the
instance] 

Developers should assume the existence of `/sbgenomics/project-files`
directory which represents the mounted directory on the reserved
instance for running the Data Studio analysis (in our case - Shiny 
app). This directory contains all project files that can be accessed and used 
within the app. 

The function itself accepts the project files directory path and fetches the 
files and their associated metadata recursively. 
The output of this helper function is a data.frame containing all files details
ready to be passed to a file picker [a link to the file picker chapter can be
added here]. 

The developers can modify the data.frame and edit its columns 
before passing it to the file picker.

Example:

```{r}
# Create mock directory on path sbgenomics/project-files to test
all_files_df <- sbShinyModules::get_all_project_files(
  path = "/sbgenomics/project-files"
)

head(all_files_df)
```
