---
title: "Load project files and their metadata"
author: "Marija Gacic"
date: "2024-07-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
# library(sbShinyModules)
```

## File loading via SBGFS in Data Studio infrastructure

This utility function for loading project files and their metadata `get_all_project_files()` is intended to be used when developing Shiny apps 
within Data Studio, or to be deployed as on-demand Shiny apps using Data Studio infrastructure.

<details>
  <summary>Data Studio File Organization</summary>
  Data Studio environments (RStudio or Jupyter) come equipped with the Seven Bridges File System (SBFS) tool installed, allowing you to access their project files right from the    IDE/Data Studio. This means that project files are mounted on the local file system and can be imported into your analysis without any download or upload.  

  The mounted directory is called sbgenomics and contains these subdirectories:  
  - project-files  
  - output-files 
  - workspace 

  The `/project-files` subdirectory contains all your project files (the project from which you started the application).

  However, the `/output-files` subdirectory aims to "save" the files you wish to write/export from your analysis/application into your project; therefore, you would have "write"      permissions here. The files you store here will be exported to the project files once you stop your analysis/application.

  The `/workspace` subdirectory can serve as a working directory where you can store temporary files produced during the app execution, which you do not want to export. The
  content of this subdirectory will be saved and available the next time the app is initialized, but we strongly suggest not storing anything here.

  This means that you should assume the existence of 
  `/sbgenomics/project-files` directory which represents the mounted directory on 
  the reserved instance for running Data Studio analysis (in our case - Shiny 
  app). This directory contains all project files that can be accessed and used 
  within the app. 
</details> 
<br>

The function accepts the project files directory path and fetches the 
files and their associated metadata recursively. 

The output of this helper function is a data.frame containing all files details
ready to be passed to a file picker [a link to the file picker chapter could be
added here].

**Note**: You can manipulate the data.frame and transform its columns before passing it to the file picker.

## Note on Dependencies 

The `get_all_project_files()` function depends on the
[xattrs package](https://github.com/hrbrmstr/xattrs)for extended attribute
support. This package is not installed automatically with ***sbShinyModules**,
so you will need to install **xattrs** separately if you wish to use this
function.

On Unix-based systems, you can install xattrs using:
```r
remotes::install_github("hrbrmstr/xattrs")
```

If you encounter installation issues, it may be due to missing system
libraries. For instance, on Ubuntu Linux, you can resolve this by installing
the `libattr1-dev` library with:
```
sudo apt-get update
sudo apt-get install libattr1-dev
```
For macOS users, additional system libraries are typically not required for
xattrs, but ensure your system is up-to-date.


Please note that the `get_all_project_files()` function is
**not available on Windows systems**. This is because it depends on the xattrs
package, which requires extended attribute functions that are not supported on
Windows.

Example of usage is presented below.

**Note:** To run this example, ensure that both the **sbShinyModules** and 
**xattrs** packages are installed. 
**Please be aware that this will not work on Windows systems.**

```{r}
# Create mock directory on path sbgenomics/project-files to test
all_files_df <- sbShinyModules::get_all_project_files(
  path = "/sbgenomics/project-files"
)

head(all_files_df)
```
